% !TEX encoding = UTF-8 Unicode
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage{xeCJK}
%\setCJKmainfont[BoldFont=STSong, ItalicFont=STKaiti]{STSong}

%\setCJKsansfont[BoldFont=STHeiti]{STXihei}
%\setCJKmonofont{STFongsong}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}
\newfontfamily\niang{HanziPenSC-W3}
\newfontfamily\song{STFangsong}

\name{\song TE. \ \ LIN} % Your name
\address{\href{https://github.com/crazyLT}{https://github.com/crazyLT}} % Your address
\address{Male \\ WenZhou ZheJiang} % Your secondary addess (optional)
\address{(86) 131-2098-5680 \\ \href{mailto:linte\_etnil@163.com}{linte\_etnil@163.com}}

\begin{document}

\begin{rSection}{OBJECTIVE}
Software Engineer.
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{EDUCATION}

\begin{rSubSubsection}{Tongji University, Shanghai \ \ \ \ Master}{Sep. 2014 - Present}
\item Computer Science and Technology. GPA: TOP 20\%
\item Core course: concrete math, machine learning.
\item Research topic model in data mining field.
\end{rSubSubsection}

\begin{rSubSubsection}{Zhejiang University of Technology, Zhejiang \ \ \ \ Bachelor}{Sep. 2010 - Jun. 2014}
\item Computer Science and Technology. GPA: TOP 20\%
\item Core course: data structures,  algorithm design, computer networks.
\end{rSubSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECT EXPERIENCE}

\begin{rSubsection}{Scoring System}{Nov. 2015 - Dec. 2015}{Web Designer \& Developer}{Tongji University}
\item A scoring system for National Technical Ability Contest of Higher Vocational Colleges.
\item Scoring system is divided into the judges and administrator module。Generate the evaluation task interface of the judges by importing the score standard file and the judges rating state display in the administrator interface real-time, at the same time monitor the abnormal score results, and then distribute the abnormal task.
\item System uses Maven to achieve package management and project construction, involved in Spring MVC, Shiro, MyBatis and other related technologies, and use WebSocket for persistent connections.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{“1st Generation of Numerical Control” in 12th Five Year Plan}{Oct. 2014}{iPad Software Developer}{Tongji University}
\item Collaboration with School of Mechanical Engineering, Tongji University.
\item Designed a control \& debug tool based iPad for manipulator arm.
\end{rSubsection}

%------------------------------------------------

\end{rSection}

\begin{rSection}{WORK EXPERIENCE}

\begin{rSubsection}{CTRIP}{Jun. 2016 - Sep. 2016}{Java Developer}{OPS Tools}
\item ITDB Project
\item Deploy a Heron real-time cluster enviroment, and consume the logs of  Kafka-MQ, design Spouts and Bolts to update the correlational infomation of employees in real-time.
\end{rSubsection}

\end{rSection}



%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & Java, C++, Python\\
Databases & MySQL\\
J2EE & Spring, Spring MVC, Shiro, Kafka, MyBatis\\
Distributed System & Docker, Mesos, Marathon\\
Tools & IDEA, Atom, GitHub\\
Foreign Language & CET-6
\end{tabular}

\end{rSection}


%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
